---
title: "HW1"
author: Megan Tebbenhoff
output: github_document
---

This is my solution for HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r_create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low","low", "mod","mod","mod","mod","high","high","high"))
)
```

Take the mean of each variable in my data frame.

```{r_mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical variable but not character or factor variable.


```{r_as.numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

I cannot convert the character variable to numeric, but I can convert the logical and factor variables as numeric. Since the logical variable is on a binary scale, it makes sense that we could calculate the mean of this set of responses, even though it would not have any meaning.

```{r_var_conversion_calculations}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

##Problem 2

```{r}

```

